Data Specialization for a Staged Lambda Calculus

### 2014-11-11 paper/implementation.tex
partway through editing section 2
added half example

Applying the rules of \cref{sec:splitting} naively can yield inefficient split programs.
In many cases, the results can be improved by considering special cases in individual rules.
For instance, trivial subterm precomputations needn't be saved at tuples:
\[
\infer {\splittwo {(e_1,e_2)} A {p,l.(r_1,r_2)}}{\splittwo {e_1} A {(),\_.r_1} & \splittwo {e_2} A {p,l.r_2}}
\]
This sort of optimization does not affect the contract of splitting at all,
because the contract only requires that there be a precomputation that the residual can accept,
with no restrictions on the form of that precomputation.
Further gains can be realized by changing the contract of splitting itself.

>>>>

Applying the rules of \cref{sec:splitting} naively can yield inefficient split programs.
In many cases, the results can be improved by considering special cases in individual rules.
For instance, trivial subterm precomputations needn't be saved at tuples:
\[
\infer {\splittwo {(e_1,e_2)} A {p,l.(r_1,r_2)}}{\splittwo {e_1} A {(),\_.r_1} & \splittwo {e_2} A {p,l.r_2}}
\]

This sort of optimization does not affect the contract of splitting at all,
because the contract only requires that there be a precomputation that the residual can accept,
with no restrictions on the form of that precomputation.
Further gains can be realized by changing the contract of splitting itself.
